**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2021-11-19 paper/manuscript.Rmd
change figure s3 legend
adjust figure S4 legend

![](figure_s3.png){height="45%"}  
**Supplemental Figure 3: Prevalence of Taxa in Samples.** Distribution of the prevalence of taxa across samples at each taxonomic level. Percent of samples is split into 10 groups where the first is for taxa present in 0 to 10% of samples, then \>10% to 20% of samples, and so on. The total number of taxa for each taxonomic level after preprocessing is in parenthesis next to the title of the plot (or the name of the taxonomic level).

@@

![](figure_s4.png){height="85%"}
**Supplemental Figure 4: Top 10 important taxa at each taxonomic level.** Summary of the 10 most important taxa for the random forest models at each taxonomic level based on the average decrease in AUROC when the feature is permuted. Dot represents the mean decrease in AUROC and the lines extending from the dot represent the standard deviation from the mean.

>>>>

![](figure_s3.png){height="45%"}  
**Supplemental Figure 3: Prevalence of Taxa in Samples.** Distribution of the prevalence of taxa across samples at each taxonomic level. Percent of samples is split into 10 groups where the first is for taxa present in 0 to 10% of samples, then \>10% to 20% of samples, and so on. The total number of taxa for each taxonomic level after preprocessing is in parenthesis next to the title of the plot.

@@

![](figure_s4.png){height="85%"}
**Supplemental Figure 4: Top 10 important taxa at each taxonomic level.** Summary of the 10 most important taxa for the random forest models at each taxonomic level based on the average decrease in AUROC when the feature is permuted. Dot represents the mean decrease in AUROC and the lines extending from the dot represent the standard deviation from the mean. Taxonomic annotations are only reliably assigned to the genus level, therefore the OTU and ASV plots have genus labels.
